---
title: "feedback_merge+clean"
output: html_document
---

```{r}
library(tidyverse)
library(igraph)
library(here)
here::i_am("./Study 1/cleaning/SSS1_Cleaning.Rmd")
```

```{r}
library(devtools)
source_url("https://raw.githubusercontent.com/JacobElder/Miscellaneous-R-Functions/master/assortativityNA.R")
```

```{r}
setwd("~/Google Drive/Volumes/")
posDf <- read.csv("./Research Project/Trait Network_Behaviral/generating network/output/adjacencyMatrix_p.csv")
posMat <- as.matrix(posDf)
posGraph <- graph.adjacency(posMat)
```

```{r}
setwd("~/Google Drive/Volumes/Research Project/")
allPosCents <- read.csv("/Volumes/GoogleDrive/My Drive/Volumes/Research Project/Trait Network_Behaviral/generating network/output/allPosCents.csv")
allNegCents <- read.csv("/Volumes/GoogleDrive/My Drive/Volumes/Research Project/Trait Network_Behaviral/generating network/output/allNegCents.csv")
allCombCents <- rbind(allPosCents, allNegCents)
allCombCents$Idx <- 1:296
allPosCents$Idx <- 1:148
```


```{r}
getwd()
rawDf <- data.table::fread( here("Study 1/raw/rawSSS.csv"))
rawDf$subID <- 1:nrow(rawDf)
```

# Inspect and remove participants who did not indicate real people as friends

```{r}
rawDf %>% select(subID , F1:F5)
```

subject 6 and 7 not real

```{r}
#test<-rawDf[!(rawDf$subID %in% c(6,7)),]
rawDf <- subset(rawDf, F1!="Good" & F2!="Like" & F4 != "Well")
rawDf <- subset(rawDf, F1!="family" & F2!="friends" & F3!="mate")
rawDf <- subset(rawDf, F4!="N/A" & F5!="N/A")
```



```{r}
tnames <- rawDf %>% select(Accurate:Worrier) %>% colnames(.)
tnamestrain<-paste0(tnames,".Train")
tnamestest<-paste0(tnames,".Test")
tnamestrainother <- paste0(tnamestrain,".F",rep(1:5, each=296))
tnamestestother <- paste0(tnamestest,".F",rep(1:5, each=296))
tnamestrainself <- paste0(tnamestrain,".Self")
tnamestestself <- paste0(tnamestest,".Self")
colnames(rawDf)[(which(colnames(rawDf)=="Accurate")):(which(colnames(rawDf)=="Accurate")+295)] <- tnamestestself
colnames(rawDf)[((which(colnames(rawDf)=="Worrier.Test.Self"))+1):(((which(colnames(rawDf)=="Worrier.Test.Self"))+1)+295)] <- tnamestrainself
colnames(rawDf)[(which(colnames(rawDf)=="Q2520")[1]):(which(colnames(rawDf)=="Q2520")[1] + 1479)] <- tnamestrainother
colnames(rawDf)[(which(colnames(rawDf)=="Q2004")):(which(colnames(rawDf)=="Q2004")+1479)] <- tnamestestother

# colnames(rawDf)[which(colnames(rawDf)=="Accurate.Train.F1"):which(colnames(rawDf)=="Worrier.Test.F5")]
# write.csv(rawDf,"~/Desktop/test.csv")
```

```{r}
SO.Df <- subset(rawDf, Order=="SelfOther")
OS.Df <- subset(rawDf, Order=="OtherSelf")
```

# Subset by Self/Other and Test/Train

```{r}
# Subset Self Train...
SelfTrain <- SO.Df %>% select(subID, Accurate.Train.Self:Witty.Train.Self)

# Subset Other Train...
OtherTrain <- OS.Df %>% select(subID, 
                               Accurate.Train.F1:Witty.Train.F1, 
                               Accurate.Train.F2:Witty.Train.F2,
                               Accurate.Train.F3:Witty.Train.F3,
                               Accurate.Train.F4:Witty.Train.F4,
                               Accurate.Train.F5:Witty.Train.F5)

# Subset Self Test...
SelfTest <- OS.Df %>% select(subID, Accurate.Test.Self:Witty.Test.Self)

# Subset Other Test...
OtherTest <- SO.Df %>% select(subID, 
                               Accurate.Test.F1:Witty.Test.F1, 
                               Accurate.Test.F2:Witty.Test.F2,
                               Accurate.Test.F3:Witty.Test.F3,
                               Accurate.Test.F4:Witty.Test.F4,
                               Accurate.Test.F5:Witty.Test.F5)
```

# Pivot grouped datasets

```{r}
#SelfTrainL <- pivot_longer(OtherTrain, cols=!subID, values_to = "eval", names_to = "trait", names_pattern = "(.*).Train.F[1-5]", values_drop_na = TRUE)

OtherTrainL <- pivot_longer(OtherTrain, cols=!subID, values_to = "eval", names_to = c("trait","friend"), names_pattern = "(.*).Train.(F[1-5])", values_drop_na = TRUE)
OtherTrainL <- merge(OtherTrainL, allCombCents, by = "trait", all.x = T)

OtherTestL <- pivot_longer(OtherTest, cols=!subID, values_to = "eval", names_to = c("trait","friend"), names_pattern = "(.*).Test.(F[1-5])", values_drop_na = TRUE)
OtherTestL <- merge(OtherTestL, allCombCents, by = "trait", all.x = T)

SelfTrainL <- pivot_longer(SelfTrain, cols=!subID, values_to = "eval", names_to = c("trait"), names_pattern = "(.*).Train.Self", values_drop_na = TRUE)
SelfTrainL <- merge(SelfTrainL, allCombCents, by = "trait", all.x = T)

SelfTestL <- pivot_longer(SelfTest, cols=!subID, values_to = "eval", names_to = c("trait"), names_pattern = "(.*).Test.Self", values_drop_na = TRUE)
SelfTestL <- merge(SelfTestL, allCombCents, by = "trait", all.x = T)
```

# Generate friend ratings

```{r}
overlapQues <- function(nameBeg, nameEnd, Df, ind = NULL){
ind1<-grep(nameBeg,colnames(Df))
ind2<-grep(nameEnd,colnames(Df))
  SGO <- grep("On", as.matrix(Df[ind,ind1:ind2]))
  if(length(SGO)==0){
    output <- NA
  }else{
    output <- SGO
  }
}

mat <- matrix(nrow=0,ncol=5)
for(i in 1:nrow(rawDf)){
  SGO <- unlist( lapply(1:5, function(x) overlapQues(nameBeg=paste0(x,"_IOS_1"),nameEnd=paste0(x,"_IOS_7"),Df=rawDf, ind = i)) )
  Close <- as.numeric( rawDf[i,paste0(1:5,"_SCI")] )
  InterS <- as.numeric( rawDf[i,paste0(1:5,"_SO")] )
  
  mat<-rbind(mat, 
        cbind(subID=rep(rawDf$subID[i],5),
              friend = c(paste0("F",1:5)),
                   SGO=SGO,
                   Close=Close,
                   InterS=InterS)
        ) 
}

friendRats <- as.data.frame(mat)
friendRats[,3:5] <- apply(friendRats[,3:5],2,as.numeric)
```

# Merge friend ratings with friend long

```{r}
OtherTrainL <- merge(OtherTrainL, friendRats, by = c("subID","friend"), all.x=T)

OtherTestL <- merge(OtherTestL, friendRats, by = c("subID","friend"), all.x=T)
```

# Flag careless task participant

```{r}
# uSubs <- unique(mergeTest$subID)
# sketchMat <- matrix(nrow=length(uSubs),ncol=5)
# for(i in 1:length(uSubs) ){
#   testSub <- subset(mergeTest, subID==uSubs[i])
#   trainSub <- subset(mergeTrain, subID==uSubs[i])
#   
#   proportionSelfs <- prop.table(table(trainSub$selfResp))
#   if(is_empty(proportionSelfs)){
#     proportionSelfs <- 1
#   }
#   proportionChoices <- prop.table(table(testSub$sideChoice))
#   if(is_empty(proportionChoices)){
#     proportionChoices <- 1
#   }
#   naSelfs <- sum(is.na(trainSub$selfResp))/length(trainSub$selfResp)
#   naChoices <- sum(is.na(testSub$sideChoice))/length(testSub$sideChoice)
#   
#   sketchMat[i, ] <- c(uSubs[i], max(proportionSelfs), max(proportionChoices), naSelfs, naChoices)
# }
# colnames(sketchMat) <- c("subID", "propSelf", "propChoice", "naSelf", "naChoice")
# sketchMat <- as.data.frame(sketchMat)
# 
# # Criteria:
# # Over 80% of same self-evaluations
# # Over 95% of same choices
# # Over 40% missing responses for self-evaluations
# # Over 40% missing responses for choices
# sketchMat$sketch <- ifelse(sketchMat$propSelf > .80 | sketchMat$propChoice > .90 | sketchMat$naSelf > .40 | sketchMat$naChoice > .40, 1, 0)
```

```{r}
indDiff <- rawDf %>% select(subID, RSE1:CESD20)
indDiff <- as.data.frame(indDiff)
```


```{r}
# Reverse code Self-Concept Clarity Scale items
SCCrevcols = c("SCC1", "SCC2", "SCC3", "SCC4", "SCC5", "SCC7",
                 "SCC8", "SCC9", "SCC10", "SCC12")
indDiff[ ,SCCrevcols] = 6 - indDiff[ ,SCCrevcols]
ind1 <- grep("SCC1", colnames(indDiff))
ind1<-min(ind1)
ind2<- grep("SCC12", colnames(indDiff))
ind2<-max(ind2)
# Compute score for Self-Concept Clarity Scale items
indDiff$SCC = rowMeans(indDiff[,ind1:ind2], na.rm = TRUE)

psych::alpha(indDiff[ind1:ind2])

psych::omega(indDiff[ind1:ind2])
```

Singelis Self-Construal
```{r}
# Compute score for Independence in Singelis Self-Construal Scale
SING.IndCol = c("SING 1", "SING 2", "SING 5", "SING 7", "SING 9", "SING 10", "SING 13",
                 "SING 15", "SING 18", "SING 20", "SING 22", "SING 24", "SING 25",
                 "SING 27", "SING 29")
indDiff$SING.Ind = rowMeans(indDiff[, SING.IndCol], na.rm = TRUE)
# Compute score for Interdependence in Singelis Self-Construal Scale
SING.InterCol = c("SING 3", "SING 4", "SING 6", "SING 8", "SING 11", "SING 12",
                   "SING 14", "SING 16", "SING 17", "SING 19", "SING 21", "SING 23",
                   "SING 26", "SING 28", "SING 30")
indDiff$SING.Inter = rowMeans(indDiff[, SING.InterCol], na.rm = TRUE)
# Compute score for Independence - Interdependence in Singelis Self-Construal Scale
indDiff$SING.IndPlus = (indDiff$SING.Ind - indDiff$SING.Inter)

psych::alpha(indDiff[SING.InterCol])
psych::alpha(indDiff[SING.IndCol])
```
Self-Esteem
```{r}
# Reverse code Rosenberg Self-Esteem items
SErevcols = c("RSE2", "RSE5", "RSE6", "RSE8", "RSE9")
indDiff[ ,SErevcols] = 5 - indDiff[ ,SErevcols]
ind1 <- grep("RSE1", colnames(indDiff))
ind1<-min(ind1)
ind2<- grep("RSE10", colnames(indDiff))
ind2<-max(ind2)
# Compute scores for Rosenberg Self-Esteem
indDiff$RSE = rowMeans(indDiff[, ind1:ind2], na.rm = TRUE)

psych::alpha(indDiff[ind1:ind2])
```

# Friendship network closeness

```{r}
# Reverse code Friendship Network Closeness items
ind1 <- grep("FNSS_1", colnames(indDiff))
ind1<-min(ind1)
ind2<- grep("FNSS_8", colnames(indDiff))
ind2<-max(ind2)
# Compute scores for Need for Cog
indDiff$FNS_C = rowMeans(indDiff[, ind1:ind2], na.rm = TRUE)

psych::alpha(indDiff[ind1:ind2])
```

# Friendhsip network socializing

```{r}
# Friendship network socializing
ind1 <- grep("FNSS_9", colnames(indDiff))
ind1<-min(ind1)
ind2<- grep("FNSS_14", colnames(indDiff))
ind2<-max(ind2)
# Compute scores for Need for Cog
indDiff$FNS_S = rowMeans(indDiff[, ind1:ind2], na.rm = TRUE)

psych::alpha(indDiff[ind1:ind2])
```

# Friendhsip network overall

```{r}
# Friendship network socializing
ind1 <- grep("FNSS_1", colnames(indDiff))
ind1<-min(ind1)
ind2<- grep("FNSS_14", colnames(indDiff))
ind2<-max(ind2)
# Compute scores for Need for Cog
indDiff$FNS = rowMeans(indDiff[, ind1:ind2], na.rm = TRUE)

psych::alpha(indDiff[ind1:ind2])
```


# UCLA Loneliness

```{r}
# Friendship network socializing
ind1 <- grep("USSS_1", colnames(indDiff))
ind1<-min(ind1)
ind2<- grep("USSS_20", colnames(indDiff))
ind2<-max(ind2)
# Compute scores for Need for Cog
indDiff$Lonely = rowMeans(indDiff[, ind1:ind2], na.rm = TRUE)

psych::alpha(indDiff[ind1:ind2])
```


# Sense of Self

```{r}
# Reverse code Sense of Self Scale items
SOSS_revcols = c("SOSS_4", "SOSS_7", "SOSS_12")
indDiff[ ,SOSS_revcols] = 6 - indDiff[ ,SOSS_revcols]
psych::alpha(indDiff[, grep("^SOSS_1$", colnames(indDiff)):grep("^SOSS_12$", colnames(indDiff))])
indDiff$SOS <- rowMeans(indDiff[, grep("^SOSS_1$", colnames(indDiff)):grep("^SOSS_12$", colnames(indDiff))], na.rm = TRUE)
```

```{r}
CESDrev <- c("CESD4","CESD8","CESD12","CESD16")
indDiff[, CESDrev] = 5 - indDiff[ ,CESDrev]
indDiff$CESD <- rowMeans(indDiff[, grep("^CESD1$", colnames(indDiff)):grep("^CESD20$", colnames(indDiff))], na.rm = TRUE)
psych::alpha(indDiff[, grep("^CESD1$", colnames(indDiff)):grep("^CESD20$", colnames(indDiff))])
psych::omega(indDiff[, grep("^CESD1$", colnames(indDiff)):grep("^CESD20$", colnames(indDiff))])
```


# Exclusions

```{r}
# indDiffs <- indDiff
# 
# sketchMat <- indDiffs %>% select(subID, Serious, UnderstandIns, UnderstandTr, Usable) %>% inner_join(sketchMat, by = "subID")
# 
# sketchMat$remove <- ifelse(sketchMat$sketch > 0 |sketchMat$Usable == 2 | sketchMat$Serious < 4, 1, 0)
```



```{r}
sigmoid <- function(feed, slope=1, shift=0){
  feed = feed - 4
  output = 1 / (1 + exp(slope * -(feed) - shift ) )
  output = (output * 6) + 1
  return(output)
}

entropy <- function(x){
  inds<-which(x!=0)
  -sum(x[inds] * log2(x[inds]))
}

computeNeighbors <- function(graph, label, type = "all"){
  curNeigh <- neighbors(graph, label, mode = type)
  curGraph <- induced.subgraph(graph, curNeigh)
  impInd <- which(!is.na(V(curGraph)$SE))
  impGraph <- induced.subgraph(curGraph, impInd)
  neighAveSE <- mean(V(impGraph)$SE, na.rm = TRUE)
  return(neighAveSE)
}

WA <- function(values, weight1=NULL, weight2=NULL, weight3=NULL){
  if( is.null(weight1) & is.null(weight2) & is.null(weight3) ){
    output <- mean(values,na.rm=T)
  }else{
    if(!is.null(weight3)){
      sum( (weight1 * weight2 * weight3) * values, na.rm=T) / sum( (weight1 * weight2 * weight3), na.rm =T )
    }else if(!is.null(weight2)){
      sum( (weight1 * weight2) * values, na.rm =T) / sum( (weight1 * weight2), na.rm =T )
      # if(any(is.na(weight2))){
      #   sum( weight1 * values) / sum( weight1 )
      # }
    }else if(!is.null(weight1)){
      sum( weight1 * values, na.rm =T) / sum( weight1, na.rm =T )
    }
  }
}
```


```{r}
for(p in 1:2){
  
  if(p==1){
    cleanTest<-SelfTestL
    cleanTrain<-OtherTrainL
  }else if(p==2){
    cleanTest<-OtherTestL
    cleanTrain<-SelfTrainL
  }
  
cleanTest$SE <- NA
cleanTest$novel <- 0
simMat <- similarity.dice(posGraph)
allPosCents$Idx <- 1:148

uSubs<-unique(cleanTest$subID)

for(i in uSubs){
  testSub <- subset(cleanTest, subID==i)
  trainSub <- subset(cleanTrain, subID==i)
  
  curNovel <- setdiff(testSub$Idx, trainSub$Idx)
  cleanTest$novel[which(cleanTest$subID==i & cleanTest$Idx %in% curNovel)] <- 1
  
  subAllSelf <- trainSub %>% select(Idx, eval) %>% arrange(Idx)
  subAllSelf <- trainSub %>% select(Idx, eval) %>% full_join(allPosCents, by = "Idx") %>% arrange(Idx)
  
  for(t in 1:nrow(testSub)){
    curSims <- simMat[trainSub$Idx, testSub$Idx[t]]
    curEval <- trainSub$eval
    curOut <- trainSub$outDegree
    curIn <- trainSub$inDegree
    
    curRem <- which(is.na(trainSub$eval))
    
    if(p==1){
      friends <- unique(trainSub$friend)
      friendSims <- lapply(friends, function(x) simMat[trainSub$Idx[which(trainSub$friend==x)], testSub$Idx[t]] )
      friendEvals <- lapply(friends, function(x) trainSub$eval[which(trainSub$friend==x)] )
    }else{
      friends <- NA
      friendSims <- NA
      friendEvals <- NA
    }
    
    if(length(curRem)>0){
      curEval <- curEval[-curRem]
      curSims <- curSims[-curRem]
      curOut <- curOut[-curRem]
      curIn <- curIn[-curRem]
    }
    
    if(p==1){
      curIOS <- trainSub$SGO
      curClose <- trainSub$Close
      curInterS <- trainSub$InterS
      
      weightedIOSAve <- WA(values=curSims, weight1 = curEval, weight2 = curIOS)
      weightedCloseAve <- WA(values=curSims, weight1 = curEval, weight2 = curClose)
      weightedInterAve <- WA(values=curSims, weight1 = curEval, weight2 = curInterS)
      friendAve <- sapply(1:5, function(x) WA(values = friendSims[[x]], weight1 = friendEvals[[x]] ) )
    
      }else if(p==2){
      
      weightedIOSAve <- NA
      weightedCloseAve <- NA
      weightedInterAve <- NA
      friendAve <- c(NA,NA,NA,NA,NA)
      
    }
    
    weightedAve <- WA(values=curSims, weight1 = curEval)
    weightedOutAve <- WA(values=curSims, weight1 = curEval, weight2 = curOut)
    weightedInAve <- WA(values=curSims, weight1 = curEval, weight2 = curIn)
    
    cleanTest$SE[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t]] <- weightedAve
    cleanTest$oSE[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t]] <- weightedOutAve
    cleanTest$iSE[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t]] <- weightedInAve
    
    cleanTest$iosSE[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t]] <- weightedIOSAve
    cleanTest$closeSE[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t]] <- weightedCloseAve
    cleanTest$interSE[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t]] <- weightedInterAve
    
    cleanTest$F1.SE[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t]] <- friendAve[1]
    cleanTest$F2.SE[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t]] <- friendAve[2]
    cleanTest$F3.SE[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t]] <- friendAve[3]
    cleanTest$F4.SE[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t]] <- friendAve[4]
    cleanTest$F5.SE[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t]] <- friendAve[5]
    
    classMat <- matrix(nrow=7,ncol=1)
    sumSims <- sum(curSims)
    for(e in 1:7){
      classIndices<-which(curEval==e)
      classIdx<-trainSub$Idx[classIndices]
      classMat[e] <- sum(simMat[classIdx,testSub$Idx[t]])/sumSims
      
    }
    cleanTest$entropy[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t]] <- entropy(classMat)
    classMat<-cbind(classMat,1:7)
    classMat <- as.data.frame(classMat)
    cleanTest$slope[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t]] <-lm(classMat$V1 ~ classMat$V2)$coefficients[[2]]
    cleanTest$er[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t]] <- sum(classMat$V1 * classMat$V2)
    
    # V(posGraph)$SE <- subAllSelf$selfResp
    
    #cleanTest$seHomoph[cleanTest$subID==i] <- assortativityNA(posGraph, V(posGraph)$SE+.001)
    
  # traitIdx <- cleanTest$Idx[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t]]
  # curLabel <- paste0("V",traitIdx)
  # 
  # cleanTest$neighAveInSE[cleanTest$subID==i & cleanTest$trialTotalT2==trialNum] <- computeNeighbors(posGraph, curLabel, "in")
  # cleanTest$neighAveOutSE[cleanTest$subID==i & cleanTest$trialTotalT2==trialNum] <- computeNeighbors(posGraph, curLabel, "out")
  # cleanTest$neighAveAllSE[cleanTest$subID==i & cleanTest$trialTotalT2==trialNum] <- computeNeighbors(posGraph, curLabel, "all")
   
  }
  
}

  if(p==1){
    SelfTestL <- cleanTest
    OtherTrainL <- cleanTrain
  }else if(p==2){
    OtherTestL <- cleanTest
    SelfTrainL <- cleanTrain
  }
  
}
```

# Exploratory: Do similarity-to-friends except separately for each friend...

```{r}
SelfTestL$friend <- NULL
SelfTestL$SGO <- NULL
SelfTestL$InterS <- NULL
SelfTestL$Close <- NULL

# SelfTestLF <- data.frame()
# for(f in 1:5){
#   SelfTestLF <- rbind(SelfTestLF, 
#         cbind(SelfTestL, friend=paste0("F",f))
#   )
# }

bindto <- lapply(1:5, function(x)  cbind(SelfTestL, friend=paste0("F",x)))
bindto
SelfTestLF <- as.data.frame(do.call(rbind, bindto))
```

# Big Version: Removing for now...

```{r}
#   
#   cleanTest<-SelfTestLF
#   cleanTrain<-OtherTrainL
#   
# cleanTest$SEf <- NA
# cleanTest$novelf <- 0
# simMat <- similarity.dice(posGraph)
# allPosCents$Idx <- 1:148
# 
# uSubs<-unique(cleanTest$subID)
# 
# for(i in uSubs){
#   testSub <- subset(cleanTest, subID==i)
#   trainSub <- subset(cleanTrain, subID==i)
#   
#   for(f in 1:5){
#     
#   friendTrain <- subset(trainSub, friend==paste0("F",f))  
#   
#   curNovel <- setdiff(testSub$Idx, friendTrain$Idx)
#   cleanTest$novelf[which(cleanTest$subID==i & cleanTest$Idx %in% curNovel)] <- 1
#   
#   subAllSelf <- friendTrain %>% select(Idx, eval) %>% arrange(Idx)
#   subAllSelf <- friendTrain %>% select(Idx, eval) %>% full_join(allPosCents, by = "Idx") %>% arrange(Idx)
#   
#   for(t in 1:nrow(testSub)){
# 
#     curSims <- simMat[friendTrain$Idx, testSub$Idx[t]]
#     curEval <- friendTrain$eval
#     curOut <- friendTrain$outDegree
#     curIn <- friendTrain$inDegree
#     
#     curRem <- which(is.na(trainSub$eval))
#     
#     if(length(curRem)>0){
#       curEval <- curEval[-curRem]
#       curSims <- curSims[-curRem]
#       curOut <- curOut[-curRem]
#       curIn <- curIn[-curRem]
#     }
#     
#     weightedAve <- WA(values=curSims, weight1 = curEval)
#     weightedOutAve <- WA(values=curSims, weight1 = curEval, weight2 = curOut)
#     weightedInAve <- WA(values=curSims, weight1 = curEval, weight2 = curIn)
#     
#     cleanTest$SEf[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t] & cleanTest$friend == paste0("F",f)] <- weightedAve
#     cleanTest$oSEf[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t]  & cleanTest$friend == paste0("F",f)] <- weightedOutAve
#     cleanTest$iSEf[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t] & cleanTest$friend == paste0("F",f)] <- weightedInAve
#     
#     classMat <- matrix(nrow=7,ncol=1)
#     sumSims <- sum(curSims)
#     for(e in 1:7){
#       classIndices<-which(curEval==e)
#       classIdx<-friendTrain$Idx[classIndices]
#       classMat[e] <- sum(simMat[classIdx,testSub$Idx[t]])/sumSims
#       
#     }
#     cleanTest$entropy[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t] & cleanTest$friend == paste0("F",f)] <- entropy(classMat)
#     classMat<-cbind(classMat,1:7)
#     classMat <- as.data.frame(classMat)
#     cleanTest$slopef[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t] & cleanTest$friend == paste0("F",f)] <-lm(classMat$V1 ~ classMat$V2)$coefficients[[2]]
#     cleanTest$erf[cleanTest$subID==i & cleanTest$Idx==testSub$Idx[t] & cleanTest$friend == paste0("F",f)] <- sum(classMat$V1 * classMat$V2)
#     
#    
#   }
#   }
#   
# }
# 
#     SelfTestLF <- cleanTest
#     OtherTrainL <- cleanTrain
```

```{r}
# SelfTestLF2 <- merge(SelfTestLF, friendRats, by = c("subID","friend"), all.x=T)
```

```{r}
nrow(subset(cleanTest, subID==uSubs[4]))
```

# Use if I use cross-vaidated predictions

```{r}
# write.csv(fullTest, "./output/fullTest.csv", row.names = F)
# write.csv(cleanTrain, "./output/fullTrain.csv", row.names = F)
# write.csv(traitFreqOverUnder, "./output/traitFreqOverUnder.csv", row.names = F)

#OtherTestLreduced <- OtherTestL %>% select(!friend) %>% select(!SGO) %>% select(!InterS) %>% select(!Close)
setdiff(colnames(OtherTestL), colnames(SelfTestL))
SelfTestL$friend <- NA
SelfTestL$SGO <- NA
SelfTestL$Close <- NA
SelfTestL$InterS <- NA
OtherTestL$Condition <- "SO"
SelfTestL$Condition <- "OS"
TestL <- rbind(OtherTestL, SelfTestL)
TestL <- TestL %>% inner_join(indDiff, by = "subID")

TestL2<-pivot_longer(TestL, cols=ends_with(".SE"), names_to = "Friend", values_to = "fSE")
TestL2$Friend <- gsub(".SE", "", TestL2$Friend)
TestL2$friend <- NULL
TestL2$Close <- NULL
TestL2$SGO <- NULL
TestL2$InterS <- NULL
TestL2 <- TestL2 %>% rename(friend = Friend)
TestL2 <- merge(TestL2, friendRats, by = c("subID","friend"))

# setdiff(colnames(SelfTestLF2),colnames(OtherTestL))
# SelfTestLF2$SE <- NULL
# SelfTestLF2$novel <- NULL
# SelfTestLF2$oSE <- NULL
# SelfTestLF2$iSE <- NULL
# SelfTestLF2$slope <- NULL
# SelfTestLF2$er <- NULL
# SelfTestLF2 <- rename(SelfTestLF2, SE = SEf, novel = novelf, oSE = oSEf, iSE = iSEf, slope = slopef, er = erf )
# SelfTestLF2$Condition <- "OS"
# TestL2 <- rbind(OtherTestL, SelfTestLF2)
# TestL2 <- TestL2 %>% inner_join(indDiff, by = "subID",all.x=T)

dir.create(here("./Study 1/cleaned/"))
arrow::write_parquet(TestL, here("./Study 1/cleaned/fullTest.parquet"))
arrow::write_parquet(TestL2, here("./Study 1/cleaned/fullTestBig.parquet"))
arrow::write_parquet(cleanTrain, here("./Study 1/cleaned/fullTrain.parquet"))
```



